### 2024-09-27 Manuscript/supplementaries.tex
added glossary

>>>>

\subsection{Glossary}

\begin{table}[ht]
\caption{Glossary and equivalence of terms used in this papers; adapted from \cite{guillerme2020shifting} and \cite{mammola2021concepts}.}
\centering
\begin{tabular}{p{4cm}p{5cm}p{5cm}p{3cm}}
Mathematics & Ecology & Macroevolution & This paper \\
\hline
Matrix ($n \times d$) with a structural relation between rows and columns & Functional space, morphospace , etc. & Morphospace, traitspace, etc. & trait space \\
\hline
Rows ($n$) & Taxa, field sites, environments, etc. & Taxa, specimen, populations, elements, OTUs etc. & observations \\
\hline
Columns ($d$) & Traits, Ordination scores, distances, etc. & Traits, ordination scores, distances, etc. & dimensions \\
\hline
Columns subset ($b \times n$; $b \leq d$) & uni/multidimensional trait; e.g. geographical location & uni/multidimensional trait; e.g. landmark coordinates & trait \\
\hline
Rows subset ($m \times d$; $m \leq n$) & Treatments, phylogenetic group (clade), etc. & Clades, geological stratum, etc. & group \\
\hline
Statistic (i.e. a measure)  & Dissimilarity index or metric, hypervolume, functional diversity, etc. & Disparity metric or index & space occupancy measure \\
\hline
\end{tabular}
\end{table}
